---
title: "UltimatumAnalysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

TO DO 
Define hypotheses / Describe variables
- Identify your model (outcome, likelihood function, predictors)
- Identify submodels for comparison
Define and motivate your priors 
- (predictive prior distribution?)
Assess model quality
- WAIC comparison
- Estimate comparison
- Predictive posterior
Report results
- Estimates and estimate interpretation
- Make sure to deal cautiously with interactions (e.g. plot!)
Compare current state of knowledge with previous
- E.g. prior vs. Posterior estimates


```{r cars}
library(pacman)
p_load(tidyverse, rethinking, pastecs, patchwork, Brobdingnag)

getwd()
locpath= getwd()
setwd(locpath)


# loading data 
d1 = read.csv("U1.csv")
d2 = read.csv("U2.csv")
d3 = read.csv("U3.csv")
d4 = read.csv("U4.csv")
d5 = read.csv("U5.csv")
d6 = read.csv("U6.csv")
d7 = read.csv("U7.csv")
d8 = read.csv("U8.csv")
d9 = read.csv("U9.csv")
d10 = read.csv("U10.csv")
d11 = read.csv("U11.csv")
d12 = read.csv("U12.csv")
d13 = read.csv("U13.csv")

# combining
d = rbind(d1, d2, d3, d4, d5, d6, d7, d8, d9, d10, d11, d12, d13)

#cleaning irrelevant columns out 
df = data.frame(d$participant.id_in_session, d$participant.payoff, d$player.id_in_group, d$player.team, d$player.age, d$player.gender, d$player.group_id, d$player.payoff, d$group.amount_offered, d$group.offer_accepted, d$subsession.round_number, d$between_group_play, d$group_number)
df = df[complete.cases(df),] 
# gender : 
# df[df$d.player.gender %in% 'Female','d.player.gender'] <- 'null' 
df <- df[, -6] 

#df$d.group.amount_offered = df>[]
#df$d.player.gender

# we don't want to scale all columns 
df_1 = data.frame(df$d.participant.id_in_session, df$d.player.id_in_group, df$d.player.team,df$d.player.group_id, df$d.group.offer_accepted, df$d.subsession.round_number, df$d.between_group_play, df$d.group_number)  # add group_number
df <- df[, -c(1,3,4,6,9,10,11,12)] # add column number for variable group number 
# standardizing the data (centering and scaling)
df_s = scale(df, center = TRUE, scale = TRUE)
df_s = as.data.frame(df_s)
# new data frame
df = cbind(df_1, df_s)

# make team condition to an integer
df$df.d.player.team = as.character(df$df.d.player.team)
df$df.d.player.team[df$df.d.player.team == '1'] = '0'
df$df.d.player.team[df$df.d.player.team == '2'] = '1'
df$df.d.player.team = as.numeric(df$df.d.player.team)

## we want to build the following models 
# amount_offered ~ condition_winning 
# amount_offered ~ condition_losing 
# ^^ done by looking at when player:id_in_group = 1, and team = 1 or 2, look at group_amount offered 

# devtools::install_github("r-lib/rlang", force = TRUE) >> doesn't work 
# why rlang_is_list not found error???? 

library(tidyverse)
library(dplyr)

# variables should be factors to function in ggplot
df$df.d.between_group_play = as.factor(df$df.d.between_group_play)
df$df.d.player.team = as.factor(df$df.d.player.team)

# trying to get pipes 
# looking at winning vs losing teams 
cond_sum = df %>%
  group_by(df.d.player.team == '1') %>% 
   summarise(offered = mean(d.group.amount_offered))
cond_sum
# very similar regardless of winning or losing 
# boxplot
p1 <- ggplot(data=df, aes(x = df.d.player.team, y = d.group.amount_offered)) +
  geom_boxplot() +
  labs(title = "Effect of team on amount offered", x = "Winning team = 1, losing team = 2", y = "Amount offered")
p1


# looking at offers between and within groups 
group_type_sum = data1 %>%
  group_by(d.between_group_play == '1') %>% 
   summarise(offered = mean(d.group.amount_offered))
group_type_sum
# here we see a bit more of a difference 
# boxplot
p2 <- ggplot(data=df, aes(x = df.d.between_group_play, y = d.group.amount_offered)) +
  geom_boxplot() + 
  labs(title = "Effect of group on amount offered", x = "Between group", y = "Amount offered")
p2

# looking at group and team effect
comb_sum = data1 %>%
  group_by(d.between_group_play == '1', d.player.team == '1') %>% 
   summarise(offered = mean(d.group.amount_offered))
comb_sum
# boxplot 
p3 <- ggplot(data=df, aes(x = df.d.between_group_play=='1', y = d.group.amount_offered, colour = df$df.d.player.team=='1')) +
  geom_boxplot() +
  labs(title = "Effect of team and group on amount offered", x = "Between group", y = "Amount offered", colour = "winning team")
p3
# looks like there is a negative effect of within group and loosing
p3a <- ggplot(data=df, aes(x = df.d.player.team=='1', y = d.group.amount_offered, colour = df$df.d.between_group_play=='1')) +
   geom_boxplot() +
   labs(title = "Effect of team and group on amount offered", x = "Winning team", y = "Amount offered", colour = "between group")
p3a

## pipes looking at ACCEPTANCE RATE

# looking at overall acceptance rates 
sum(data1$d.group.offer_accepted == '1')
sum(data1$d.group.offer_accepted == '0')

# look at this as a function of the offer 

# winning or losing rate of acceptance 
team_cond_rate = data1 %>%
  group_by(d.player.team == '1') %>% 
   summarise(accept_rate = sum(d.group.offer_accepted == '1'))
team_cond_rate
# boxplot
df$df.d.between_group_play = as.factor(df$df.d.between_group_play)
df$df.d.player.team = as.factor(df$df.d.player.team)

p4 <- ggplot(df, aes(df.d.group.offer_accepted, ..count..)) +
  geom_bar(aes(fill = sum(df.d.group.offer_accepted == '1')), position = "dodge"))
  
 # labs(title = "Effect of group on amount offered", x = "Between group", y = "Amount offered")
p4


# very similar regardless of winning or losing 
team_cond_rate1 = data1 %>%
  group_by(d.player.team == '1') %>% 
   summarise(accept_rate = sum(d.group.offer_accepted == '0'))
team_cond_rate1


# looking at offers between and within groups 
group_type_rate = data1 %>%
  group_by(d.between_group_play == '1') %>% 
   summarise(accept_rate =  sum(d.group.offer_accepted == '1'))
group_type_rate

group_type_rate1 = data1 %>%
  group_by(d.between_group_play == '1') %>% 
   summarise(accept_rate =  sum(d.group.offer_accepted == '0'))
group_type_rate1

# combining all 
comb_rate = data1 %>%
  group_by(d.between_group_play == '1', d.player.team == '1') %>% 
   summarise(accept_rate = sum(d.group.offer_accepted == '1'))
comb_rate

comb_rate1 = data1 %>%
  group_by(d.between_group_play == '1', d.player.team == '1') %>% 
   summarise(accept_rate = sum(d.group.offer_accepted == '0'))
comb_rate1


## MODELZZZZZ 

# amount_offered ~ team_in_group 
# amount_offered ~ team_out_group 
# done by id_in_group = 1, and condition team = 1 (in), or 0 (out)

# amount_offered ~ condition + team 
# amount_offered ~ condition*team 

# acceptance_rate ~ condition 
# acceptance_rate ~ team 
# acceptance_rate ~ condition + team 
# acceptance_rate ~ condition*team 

# Step 1, add column to csv files 
# Step 2, Merge and load data files,
# Step 3,  Clean data files 
# Step 4 - check out the data (see results)
# step 5 - build bayesian models, see what we can predict 


# MONEY OFFERED MODELS 
# model for amount offered 
# model for effect of condition (player team) with radom effects of (participant ID (participant_id_in_session), experiment number (group number) & intercept)

m1 <- map(
  alist(
    d.group.amount_offered ~ dnorm( mu , sigma ) , 
    mu <- ai + a[df.d.participant.id_in_session] + ab[df.d.group_number] + bA*df.d.player.team ,
    ai ~ dnorm(0, 1) , 
    a[df.d.participant.id_in_session] ~ dnorm( 0 , 1 ) , 
    ab[df.d.group_number] ~ dnorm(0, 1), 
    bA ~ dnorm( 1 , 0.2) , 
    sigma ~ dunif( 0 , 3 )
 ) ,  
 data = df)

precis(m1)
devtools::install_github("rmcelreath/rethinking", force = TRUE)
plot(precis(m1))

# because this is the best model we want to make a predictive posterior plot:
# Plot observations against predictions 
mu <- link(m1, na.rm = TRUE)
# summarize samples across cases
mu.mean <- apply( mu , 2 , mean )
mu.PI <- apply( mu , 2 , PI )
# simulate observations
# again no new data, so uses original data
model.sim <- sim( m1 , n=1000, na.rm = TRUE )
model.PI <- apply( model.sim , 2 , PI  )

# plot predictions against observed 
plot( mu.mean ~ df$d.group.amount_offered, col=rangi2 , ylim=range(mu.PI) ,
    xlab="Observed amount offered" , ylab="Predicted amount offered" )
abline( a=0 , b=1 , lty=2 )
for ( i in 1:nrow(df) )
    lines( rep(df$d.group.amount_offered[i],2) , c(mu.PI[1,i],mu.PI[2,i]) ,
        col=rangi2 )

########

#extracting samples from the posterior
post.samples=extract.samples(m1)

#plotting with the uncertainty
#just to check if the model makes sense
plot( d.group.amount_offered ~ df.d.player.team , df)
abline(a=coef(m1)['a'], b=coef(m1)['b'])
for ( i in 1:1000 )
abline( a=post.samples$a[i] , b=post.samples$b[i] , col=col.alpha(rangi2, 0.5) )




# posterior certainty check 
# extract 20 samples from the posterior
post <- extract.samples( m1 , n= 1000)
# display raw data and sample size
plot(df$d.group.amount_offered ~ df$df.d.player.team,
xlim=range(df$df.d.player.team) , ylim=range(df$d.group.amount_offered) ,
col=rangi2 , xlab="Team Condition" , ylab="Amount Offered" )
# plot the lines, with transparency
for ( i in 1:1000)
abline( a=post$a[i] , b=post$b[i] , col=col.alpha("purple",0.3) )

###### 


m2 <- rethinking::map(
  alist(
    d.group.amount_offered ~ dnorm( mu , sigma ) , 
    mu <- ai + a[df.d.participant.id_in_session]+ ab[df.d.group_number] + bB*df.d.between_group_play,
    ai ~ dnorm(0, 1) , 
    a[df.d.participant.id_in_session] ~ dnorm( 0 , 1) , 
    ab[df.d.group_number] ~ dnorm(0, 1), 
    bB ~ dnorm( 1 , 0.2) , 
    sigma ~ dunif( 0 , 3 )
 ) ,  
 data = df)

precis(m2)
devtools::install_github("rmcelreath/rethinking", force = TRUE)

plot(precis(m2))


# model with both added together 
m3 <- rethinking::map(
  alist(
    d.group.amount_offered ~ dnorm( mu , sigma ) , 
    mu <- ai + a[df.d.participant.id_in_session] + ab[df.d.group_number] + bA*df.d.player.team + 
      bB*df.d.between_group_play,
    ai ~ dnorm(0, 1) , 
    a[df.d.participant.id_in_session] ~ dnorm( 0 , 1 ) , 
    ab[df.d.group_number] ~ dnorm(0, 1), 
    bA ~ dnorm( 1 , 0.2) , 
    bB ~ dnorm(1, 0.2) , 
    sigma ~ dunif( 0 , 3 )
 ) ,  
 data = df)

precis(m3)
devtools::install_github("rmcelreath/rethinking", force = TRUE)

plot(precis(m3))


# model with interaction of the two 
m4 <- rethinking::map(
  alist(
    d.group.amount_offered ~ dnorm( mu , sigma ) , 
    mu <- ai + a[df.d.participant.id_in_session] + ab[df.d.group_number] + bA*df.d.player.team + bB*df.d.between_group_play + bAB*df.d.player.team*df.d.between_group_play, 
    ai ~ dnorm(0, 1) , 
    a[df.d.participant.id_in_session] ~ dnorm( 0 , 1) , 
    ab[df.d.group_number] ~ dnorm(0, 1), 
    bA ~ dnorm( 1 , 0.2) , 
    bB ~ dnorm(1, 0.2) ,
    bAB ~ dnorm(1, 0.2), 
    sigma ~ dunif( 0 , 3 )
 ) ,  
 data = df)

precis(m4)

devtools::install_github("rmcelreath/rethinking", force = TRUE)
plot(precis(m4))

# making a WAIC comparison to choose the best model 
(amount_offered_models <- compare(m1, m2, m3, m4))

# WAIC plot
plot(amount_offered_models , SE = TRUE , dSE = TRUE )

#beta difference 
coeftab(m1, m2, m3, m4)

# coeftab plot 
plot(coeftab(m1, m2, m3, m4))

#?coeftab_plot - the way to do it without rethinking) 
beta <- coeftab(m1, m2, m3, m4)
pars <- c("ai", "bA","bB","bAB","sigma")
coeftab_plot(beta, NULL , pars, col.ci="rosybrown4", by.model=FALSE , prob=0.89)



### MODELS GROUP OFFER ACCEPTED 
# for offer accepted, binomial distirbution with an interaction and look at rate of binomial distribution (is defined a linear model, same as in amount offered) + interaction 

# m5, variable team conidtion 
#library(rethinking)
df_5 = data.frame(df$df.d.participant.id_in_session, df$df.d.group_number, df$df.d.group.offer_accepted, df$df.d.player.team)
library(plyr)
df_5 = rename(df_5, c("df.df.d.participant.id_in_session"="ID", "df.df.d.group_number"="GroupNumber", "df.df.d.group.offer_accepted"="AcceptanceRate", "df.df.d.player.team"="Team"))
#str(df_5)
df_5$ID = as.numeric(df_5$ID)
df_5$GroupNumber = as.numeric(df_5$GroupNumber)
df_5$AcceptanceRate = as.numeric(df_5$AcceptanceRate)
df_5$Team = as.numeric(df_5$Team)

m5 <- map2stan( 
alist(
  AcceptanceRate ~ dbinom( 26 , p ) , 
  logit(p) <- ai + a[ID] + ab[GroupNumber] + bA*Team,
  ai ~ dnorm(0,1),
  a[ID] ~ dnorm(0,1),
  ab[GroupNumber] ~ dnorm(0,1), 
  bA ~ dnorm(0, 0.2),
  sigma ~ dunif(0,3)
 ), 
data=df_5 , chains=2 , cores = 2, iter= 5000 , warmup=2000)
precis(m5)
precis(m5, depth = 2)

devtools::install_github("rmcelreath/rethinking", force = TRUE)
#pairs(m5)
plot(precis(m5))

# m6, variable between group play 
df_6 = data.frame(df$df.d.participant.id_in_session, df$df.d.group_number, df$df.d.group.offer_accepted, df$df.d.between_group_play)
#library(plyr)
df_6 = rename(df_6, c("df.df.d.participant.id_in_session"="ID", "df.df.d.group_number"="GroupNumber", "df.df.d.group.offer_accepted"="AcceptanceRate", "df.df.d.between_group_play"="BetweenGroup"))
#str(df_6) 
df_6$ID = as.numeric(df_6$ID)
df_6$GroupNumber = as.numeric(df_6$GroupNumber)
df_6$AcceptanceRate = as.numeric(df_6$AcceptanceRate)
df_6$BetweenGroup = as.numeric(df_6$BetweenGroup)


m6 <- map2stan( 
alist(
  AcceptanceRate ~ dbinom( 26 , p ) , 
  logit(p) <- ai + a[ID] + ab[GroupNumber] + bp*BetweenGroup,
  ai ~ dnorm(0,1),
  a[ID] ~ dnorm(0,1),
  ab[GroupNumber] ~ dnorm(0,1), 
  bp ~ dnorm(0, 0.2),
  sigma ~ dunif(0,3)
 ), 
data=df_6 , chains=2 , cores = 2, iter= 5000 , warmup=2000)

precis(m6)
precis(m6, depth = 2)
devtools::install_github("rmcelreath/rethinking", force = TRUE)
plot(precis(m6))
plot(m6)

# extract Stan samples
post <- extract.samples(m6)
# Plot observations against predictions 
mu <- link(m6, na.rm = TRUE)
# summarize samples across cases
mu.mean <- apply( mu , 2 , mean )
mu.PI <- apply( mu , 2 , PI )
# simulate observations
# again no new data, so uses original data
model.sim <- sim( m6 , n=1000, na.rm = TRUE )
model.PI <- apply( model.sim , 2 , PI  )

# plot predictions against observed 
plot( mu.mean ~ df_6$AcceptanceRate, col=rangi2 , ylim=range(mu.PI) ,
    xlab="Observed acceptance rate" , ylab="Predicted acceptance rate" )
abline( a=0 , b=1 , lty=2 )
for ( i in 1:nrow(df_6) )
    lines( rep(df_6$AcceptanceRate[i],2) , c(mu.PI[1,i],mu.PI[2,i]) ,
        col=rangi2 )

# m7, model on between group play + team condition 
df_7 = data.frame(df$df.d.participant.id_in_session, df$df.d.group_number, df$df.d.group.offer_accepted, df$df.d.between_group_play, df$df.d.player.team)
#library(plyr)
df_7 = rename(df_7, c("df.df.d.participant.id_in_session"="ID", "df.df.d.group_number"="GroupNumber", "df.df.d.group.offer_accepted"="AcceptanceRate", "df.df.d.between_group_play"="BetweenGroup", "df.df.d.player.team"="Team"))
df_7$ID = as.numeric(df_7$ID)
df_7$GroupNumber = as.numeric(df_7$GroupNumber)
df_7$AcceptanceRate = as.numeric(df_7$AcceptanceRate)
df_7$BetweenGroup = as.numeric(df_7$BetweenGroup)
df_7$Team = as.numeric(df_7$Team)

m7 <- map2stan( 
alist(
  AcceptanceRate ~ dbinom( 26 , p ) , 
  logit(p) <- ai + a[ID] + ab[GroupNumber] + bp*BetweenGroup + bq*Team,
  ai ~ dnorm(0,1),
  a[ID] ~ dnorm(0,1),
  ab[GroupNumber] ~ dnorm(0,1), 
  bp ~ dnorm(0, 0.2),
  bq ~ dnorm(0, 0.2),
  sigma ~ dunif(0,3)
 ), 
data=df_7 , chains=2 , cores = 2, iter= 5000 , warmup=2000)

precis(m7)
precis(m7, depth = 2)
# devtools::install_github("rmcelreath/rethinking", force = TRUE)
plot(precis(m7))

# m8, model on between group play*team condition 
df_8 = data.frame(df$df.d.participant.id_in_session, df$df.d.group_number, df$df.d.group.offer_accepted, df$df.d.between_group_play, df$df.d.player.team)
#library(plyr)
df_8 = rename(df_8, c("df.df.d.participant.id_in_session"="ID", "df.df.d.group_number"="GroupNumber", "df.df.d.group.offer_accepted"="AcceptanceRate", "df.df.d.between_group_play"="BetweenGroup", "df.df.d.player.team"="Team"))
df_8$ID = as.numeric(df_8$ID)
df_8$GroupNumber = as.numeric(df_8$GroupNumber)
df_8$AcceptanceRate = as.numeric(df_8$AcceptanceRate)
df_8$BetweenGroup = as.numeric(df_8$BetweenGroup)
df_8$Team = as.numeric(df_8$Team)

m8 <- map2stan( 
alist(
  AcceptanceRate ~ dbinom( 26 , p ) , 
  logit(p) <- ai + a[ID] + ab[GroupNumber] + bp*BetweenGroup + bq*Team + br*Team*BetweenGroup,
  ai ~ dnorm(0,1),
  a[ID] ~ dnorm(0,1),
  ab[GroupNumber] ~ dnorm(0,1), 
  bp ~ dnorm(0, 0.2),
  bq ~ dnorm(0, 0.2),
  br ~ dnorm(0, 0.2),
  sigma ~ dunif(0,3)
 ), 
data=df_8 , chains=2 , cores = 2, iter= 5000 , warmup=2000)

precis(m8)
precis(m8, depth = 2)
# devtools::install_github("rmcelreath/rethinking", force = TRUE)
plot(precis(m8))


# making a WAIC comparison to choose the best model 
compare(m5, m6, m7, m8)

#beta difference 
coeftab(m5, m6, m7, m8)

# WAIC plot
plot(compare(m5, m6, m7, m8))

# coeftab plot 
plot(coeftab(m5, m6, m7, m8))


```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
# want boxplots maybe? how do we get this of pipes? 
# boxplots 
# plots of model predictions 
# plots of likelihood functions 
# anything else? 
# do we want posterior predictive plots maybe? 
# plot simulated posteriors against actual posteriors, do we want this? 

## BOXPLOTS 
library(ggplot2)
# df = is.numeric(df) >> doesnt work 

# boxplots for fun & games 
ggplot(df, aes(df.d.group.amount_offered, colour = df.d.player.team)) + geom_boxplot

ggplot(data1, aes(df.d.group.amount_offered, colour = df.d.between_group_play)) + geom_boxplot

# maybe facet wrap



gggplot = function(model, x = NULL , y = NULL, dataframe){ 
   #where: 
  #model is a model resulting from MAP 
  #x is the x variable as a string (can be left unspecified) 
  #y is the y variable as a string (can be left unspecified) 
  #dataframe is the dataframe from which the model is trained upon 
  #requires packages: dplyr, ggplot2, stringr and rethinking
  
  if (is.null(y) == T){ 
    #if y isn't specified - extract y 
    temp <- flist_untag(model@formula)[[1]] 
    y <- as.character(temp[[2]])
    } 
  if (is.null(x) == T){ 
    #if x isn't specified - extract x 
      temp <- flist_untag(model@formula)[[2]] 
      x <- gsub(" ","",gsub(".*\\*","",as.character(temp[[3]])[3])) 
  }
  
   #extracting data from the dataframe 
  xd <- dplyr::select(dataframe, x) 
  yd <- dplyr::select(dataframe, y)
  
   #calculate the prior data 
  post <- extract.samples(model) 
  #posterior from samples 
  mu.link <- function(x) post$a + post$b*x 
  VIQ.seq <- seq( from=min(xd) , to=max(xd) , by=0.1 ) 
  mu <- sapply( VIQ.seq , mu.link ) 
  mu.mean <- apply( mu , 2 , mean ) 
  mu.HPDI <- apply( mu , 2 , HPDI , prob=0.89 ) 
  temp_list = list(VIQ.seq); names(temp_list) <- x 
  #naming the vector in the list (since the sim function requires it) 
  sim.VIQ <- sim( model , data=temp_list ) 
  VIQ.PI <- apply( sim.VIQ , 2 , PI , prob=0.89 )

  #transform the data from ggplot 
    #for making the line 
  temp_df <- data.frame(VIQ.seq = VIQ.seq, mu.mean = mu.mean) 
  #for making the HDPI 
  temp_matrix <- t(data.frame(mu.HPDI = mu.HPDI)) 
  #t() is a tranpose function which returns a matrix 
  temp_df1 = data.frame(lower = temp_matrix[,1], upper = temp_matrix[,2], mu.mean = mu.mean, VIQ.seq = VIQ.seq)
   #for making the PI 
  temp_matrix <- t(data.frame(VIQ.PI = VIQ.PI)) 
  temp_df2 = data.frame(lower = temp_matrix[,1], upper = temp_matrix[,2], mu.mean = mu.mean, VIQ.seq = VIQ.seq) 
  #for the points 
  dataframe = data.frame(xd, yd) 
  #taking the data to new column as to chose the name (maintaining old name for the names on the plot) 
  dataframe$c1 = dataframe[,1] 
  dataframe$c2 = dataframe[,2]
  
   #make the plot 
  grob = ggplot(dataframe, aes(x = c1, y = c2)) + 
    geom_ribbon(data = temp_df2, aes(x = VIQ.seq, y = mu.mean, ymin = lower, ymax = upper), fill = "grey70", alpha = 2/3) + 
    geom_ribbon(data = temp_df1, aes(x = VIQ.seq, y = mu.mean, ymin = lower, ymax = upper), fill = "grey83", alpha = 2/3) + 
    geom_line(data = temp_df, aes(x = VIQ.seq, y = mu.mean))+ 
    geom_point(color = "navyblue", shape = 1, size = 1.5, alpha = 2/3)+ 
    xlab(colnames(dataframe)[1]) + 
    ylab(colnames(dataframe)[2]) 
  #using the names for the axis 
  return(grob) 
  } #go go gadget fancy plot

df$d.player.team = as.numeric(df$d.player.team)
df$d.group.amount_offered = as.numeric(df$d.group.amount_offered)
str(df)

#plotting predictions
p_1 = gggplot(m1, x = df$df.d.player.team, y = df$d.group.amount_offered, dataframe = df) +
  ggtitle("Model 1")
p_1 
#plotting predictions
df = as.data.frame(df)
gggplot(m1, dataframe = df) +
  ggtitle("Model 1")
p.1

cor(df$df.d.player.team, df$df.d.player.team)
cor


#########
#jjnkjnj
chimp.ensemble <- ensemble(m5,m6,m7,m8, )
# empty plot frame with good axes
plot( 0 , 0 , type="n" , xlab="prosoc_left/condition" ,
    ylab="proportion pulled left" , ylim=c(0,1) , xaxt="n" ,
    xlim=c(1,4) )
axis( 1 , at=1:4 , labels=c("0/0","1/0","0/1","1/1") )
# plot raw data, one trend for each of 7 individual chimpanzees
# will use by() here; see Overthinking box for explanation
p <- by( d$pulled_left ,
    list(d$prosoc_left,d$condition,d$actor) , mean )
for ( chimp in 1:7 )
    lines( 1:4 , as.vector(p[,,chimp]) , col=rangi2 , lwd=1.5 )
# now superimpose posterior predictions
lines( 1:4 , pred.p )
shade( pred.p.PI , 1:4 )

### 

identify( x=df$d.group.amount_offered , y=mu.mean , labels=df$df.d.player.team , cex=0.8 )

# compute residuals
amount.resid <- df$d.group.amount_offered - mu.mean
# get ordering by divorce rate
o <- order(amount.resid)
# make the plot
dotchart( amount.resid[o] , labels=df$Loc[o] , xlim=c(-6,5) , cex=0.6 )
abline( v=0 , col=col.alpha("black",0.2) )
for ( i in 1:nrow(d) ) {
    j <- o[i] # which State in order
    lines( df$d.group.amount_offered[j]-c(mu.PI[1,j],mu.PI[2,j]) , rep(i,2) )
    points( d$d.group.amount_offered[j]-c(amount.PI[1,j],amount.PI[2,j]) , rep(i,2)),
    }
    pch=3 , cex=0.6 , col="gray" )

##############
fancypantsplot <- function(model, x, y, dataframe) {
 #extracting data from the dataframe 
  xd <- dplyr::select(dataframe, x) 
  yd <- dplyr::select(dataframe, y)
  
  #calculate the prior data - the next 4 lines basically recreate the link function (see page 107)
  post <- extract.samples(model) 
  mu.link <- function(x) post$a + post$b*x 
  x.seq <- seq( from=min(xd) , to=max(xd) , by=0.1 ) 
  mu <- sapply( x.seq , mu.link ) 
  #summarize the distribution of mu
  mu.mean <- apply( mu , 2 , mean ) 
  mu.HPDI <- apply( mu , 2 , HPDI , prob=0.89 ) 
  
  temp_list = list(x.seq); names(temp_list) <- x  #naming the vector in the list (since the sim function apparently  requires it - thank Kenneth)
  sim.x <- sim( model , data=temp_list ) 
  x.HPDI <- apply( sim.x , 2 , HPDI , prob=0.89 )
  
  #creating dataframe containing only the x and y values
  new_df = data.frame(xd, yd)
  #giving the columns new names that can be called in the plot function
  names(new_df) <- c('x1', 'y1')
  # plot raw data
  plot( y1 ~ x1 , new_df, col=col.alpha(rangi2,0.5) )
  # draw MAP line
  lines( x.seq , mu.mean )
  # draw HPDI region for line
  shade( mu.HPDI , x.seq )
  # draw HPDI region for simulated heights
  shade( x.HPDI , x.seq )
}

#IN ACTION!
fancypantsplot(m1, 'df.d.player.team', 'd.group.amount_offered', df)


########


#extracting samples from the posterior
post.samples=extract.samples(m1)

#plotting with the uncertainty
#just to check if the model makes sense
plot(d.group.amount_offered ~ df.d.player.team, df)
abline(a=coef(m1)['a'], b=coef(m1)['b'])
for ( i in 1:1000 )
abline( a=post.samples$a[i] , b=post.samples$b[i] , col=col.alpha(rangi2, 0.5) )
#seems quite alright

# define sequence of weights to compute predictions for 
# these values will be on the horizontal axis
df.d.player.team.seq <- seq( from=-2 , to=2.5 , by=0.1 )

# use link to compute mu for each sample from posterior and for each value in scaleVIQ.seq
mu <- link( m1 , data=data.frame(df.d.player.team=df.d.player.team.seq) )

t(HPDI(d$ADOS))
# use type="n" to hide raw data
plot( ScaleADOS ~ ScaleVIQ , d , type="n" )
# loop over samples and plot each mu value
for ( i in 1:nrow(mu) )
points( ScaleVIQ.seq , mu[i,] , pch=16 , col=col.alpha(rangi2,0.1) )

#summarize the distribution of mu
mu.mean <- apply( mu , 2 , mean )
mu.HPDI <- apply( mu , 2 , HPDI , prob=0.89 )

# plot raw data
# fading out points to make line and interval more visible
plot( ScaleADOS ~ ScaleVIQ , data=d , col=col.alpha(rangi2,0.5) )
# plot the MAP line, aka the mean mu for each weight
lines( ScaleVIQ.seq , mu.mean )
# plot a shaded region for 89% HPDI
shade( mu.HPDI , ScaleVIQ.seq )

#simulating ADOS values for the specific VerbalIQ values in the previously defined sequence
sim.ados <- sim( m1.1 , data=list(ScaleVIQ=ScaleVIQ.seq) )
#summarizing the distribution of the simulation
ados.HPDI <- apply( sim.ados , 2 , HPDI , prob=0.89 )

# plot raw data
plot( ScaleADOS ~ ScaleVIQ , d , col=col.alpha(rangi2,0.5) )
# draw MAP line
lines( ScaleVIQ.seq , mu.mean )
# draw HPDI region for line
shade( mu.HPDI , ScaleVIQ.seq )
# draw PI region for simulated heights
shade( ados.HPDI , ScaleVIQ.seq )



############

#plotting likelihood (remake to exam data)
df1 = subset(df$df.d.player.team == 1)
# NO SUBSET FUCKING FUNCTION WORKING ????????????????????

dens(df$d.group.amount_offered, col='red')
dens(df$d.group.amount_offered[df$d.player.team == "2"], add = T)

dens(dataS$d.group.amount_accepted[dataS$d.player.team == "1"], col='red')
dens(dataS$d.group.amount_accepted[dataS$d.player.team == "2"], add = T)

dens(dataS$d.group.amount_offered[dataS$d.between_group_play == "1"], col='red')
dens(dataS$d.group.amount_offered[dataS$d.between_group_play == "0"], add = T)

dens(dataS$d.group.amount_accepted[dataS$d.between_group_play == "1"], col='red')
dens(dataS$d.group.amount_accepted[dataS$d.between_group_play == ""], add = T)


#plotting liklihood distributions (ggplot) 
ggplot(df, aes(x = df.d.group.amount_offered, color = df.d.player.team)) + 
  geom_density()

# best of the models run predicted posterior and compare 


# model uncertainty?? (Portfolio 3)
#plotting with the uncertainty
#just to check if the model makes sense
plot(ScaleADOS ~ ScaleSIQ, d)
abline(a=coef(m1.1)['a'], b=coef(m1.1)['b'])
for ( i in 1:1000 )
abline( a=post.samples$a[i] , b=post.samples$b[i] , col=col.alpha(rangi2, 0.5) )
#doesn't look that great - most SIQ values cluster quite low on the scale





```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
