---
title: "Imitation_inhibition_exp"
author: "Astrid L."
date: "16/2/2018"
output: html_document
---

Imitation-inhibition experiment 
```{r}

getwd()
locpath= getwd()
setwd(locpath)

library(pacman)
p_load(plyr, dplyr, stringr, tidyverse, tidyr, ggplot2, pastecs, lmerTest, MuMIn, lme4, modelr, Metrics, caret, ddalpha, ggplot2, pastecs, crqa, lmerTest, pROC, modelr) # choose n (y/n?) in ddalpha

data <- read.csv("~/Desktop/4. semester/Soc_Cult/imitation_inhibition_data.csv")
```

1) hypothesis
2) plot
3) analysis

Hypothesis:
We hypothsize that RT’s are shorter when there is congruency between image and task (maybe: also less errors)

accuracy (acc) > congr
RT< congr

```{r cars}
correctnessframe = data %>%
  group_by(Participant, Congruity, Order_number) %>%
  dplyr::summarise(Number_correct = sum(Correctness)totalN = n)
```

We want to remove RT's that aren't possible (negatives and too small)
<RT<
300 miliseconds is what books recommend that is the fastest we can react
Riccardo said sometimes use 200 (check within participant, did an experiment where they removed the lower 25% of RTs)
2 s max 

a study like this could be a good exmample of a study where it could be a good idea to run a pilot to set these fixed values for min and max RT's etc. 


```{r pressure, echo=FALSE}
# does congruenty affect answer?
ggplot(data, aes(Congruity, as.numeric(Correctness)geom_bar())

# linking this to RT's we can see that people are slower when there IS congruency 
       
       
```


